Two years of CiTO annotations

### 2022-08-28 article.Rmd
Proper markdown for figure captions

![](images/datamodel.png)
**Figure 1**: Screenshot of the citation statements for an article where the
*objective of project or action* qualifier is used to annotate the citation with their
CiTO intentions.

@@

![](images/scholiaStats.png)
**Figure 2**: XXXX.

>>>>

![Screenshot of the citation statements for an article where the
*objective of project or action* qualifier is used to annotate the citation with their
CiTO intentions.](images/datamodel.png)

@@

![Screenshot of the Scholia Citation Typing Ontology page showing the
daily statistics.](images/scholiaStats.png)
